Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
adding a lot on characterizing block sources

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

@@

\begin{definition}
Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
\end{definition}

@@

%\begin{claim}
%Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
%\end{claim}
\bnote{I instead of min-entropy here we want support size.  Are we okay with that?  Not sure how this adapts to average min-entropy.}
\begin{proof}
For convenience relabel the ordering that violates the condition as $1,..., \ell$.  We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.  As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.  Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.  This process is repeated until $W_{\ell-\beta+1}$ is learned.  Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct $W_i | W_1,.., W_{i-1}$.
\end{proof}

>>>>

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $|W|$ be the size of the support of $W$ that is $|W| = \{w | \Pr[W=w]>0\}$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

@@

\begin{definition}
Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{jump} of a block $i_j$ is $J(i_j) = \max|W_{i_j} |$ conditioned on the values $W_{i_1},..., W_{i_{j-1}}$.
\end{definition}

@@

\begin{proof}
For convenience relabel the ordering that violates the condition as $1,..., \ell$.  We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.  As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.  Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.  This process is repeated until $W_{\ell-\beta+1}$ is learned.  Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct the support of $W_i | W_1,.., W_{i-1}$.
\end{proof}
